Supplementary information

### 2019-12-12 manuscript/supplementary.Rmd
added new composite crown descriptor names to manuscript
fixed importance plots

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Relative descriptor Gini importances measures.',fig.height=5}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```

@@

>>>>

```{r site_differences,fig.cap='Differences between sites in phenotypic descriptors analysed by supervised Random Forest. a) Multidimensional scaling (MDS) plot of random forest proximity values of individual trees scaled to two dimensions. Mean margin value shown. b) Relative descriptor Gini importances measures.',fig.height=6}
loadd(site_differences_mds_plot)
grid.arrange(site_differences_mds_plot$a,site_differences_mds_plot$b,nrow = 1)
```

@@

\newpage
